Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-08-31 prevalence_testing/postshocktest2021draft.tex
addition of proof

>>>>

\begin{prop}
  Let $p_i \sim \mc{D}$ be independent sequence of p-values for $i = 1, \ldots, n+1$ and some distribution $\mc{D}$, where $p_1$ is the p-value of the time series of interest. Let  $\alpha$ denote the significance level. If $\P(p_1 \leq \alpha) \neq 0.5$, with probability one, the expected misclassification rate for voting in prevalence testing is
  \begin{align*}
    \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases} .
  \end{align*}
\end{prop}

\begin{proof}
 Since $\P(p_1 \leq \alpha)\in \reals$, by Strong Law of Large Numbers,
\begin{align*}
  \frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha)  
   \stackrel{a.s.}{\rightarrow}  \P(p_i \leq \alpha) = \P(p_1 \leq \alpha),
\end{align*}
which follows from the fact that $p_i$ are i.i.d. Define
\begin{align*}
  f \colon [0,1] \mapsto \{0,1\} 
  \text{ with }
  f(x) = I(x \geq 0.5).
\end{align*}
Let $C(f)$ denote the continuity set of $f$. Suppose that $\P(p_1 \leq  \alpha) \neq 0.5$. In this case, notice that 
\begin{align*}
  \P(\P(p_1 \leq  \alpha) \in C(f)) =1.
\end{align*}
By Slutsky's Theorem, we have
\begin{align*}
  I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
  \stackrel{a.s.}{\rightarrow} 
  I\{ \P(p_1 \leq  \alpha) \geq 0.5\}.
\end{align*}
Moreover, note that
\begin{align*}
\E \left\{ |I\{ \P(p_1 \leq  \alpha) \geq 0.5\}
  - I( p_1 \leq  \alpha) |\right\}
  & = \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases} \\
  & \leq  0.5.
\end{align*}
That implies that with probability one, 
\begin{align*}
  \E \left\{ \left|I\left\{\frac{1}{n}\sum_{i=2}^{n+1}I(p_i \leq  \alpha) \geq 0.5\right\}
  - I( p_1 \leq  \alpha) \right|\right\}
  = \begin{cases}
    1- \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) > 0.5 \\
    \P(p_1 \leq \alpha) & \text{ if } \P(p_1 \leq \alpha) < 0.5 
  \end{cases}.
\end{align*}
That is, with probability one, the expected misclassification rate is as above.
\end{proof}

\begin{remark}
  Since indicator functions are bounded in $\mc{L}^2$, by Chebyshev-Rachman Strong Law of Large Numbers, the independence assumption can be relaxed to be that those p-values are uncorrelated.
\end{remark}
